\myTitle

### 2014-08-20 tex/main-body-text.tex
Add acknowledgments and fix "deterministic" statements.
Closes #2 and #3.

However, here we identify 
the close relationship between {\sc flock}'s algorithm and the program
{\sc structure}.  Although the algorithm in {\sc flock}
is, as the authors point out, entirely deterministic, it can be interpreted as a 
limiting case of a probabilistic search algorithm applied to one of {\sc structure}'s
models.  More specifically, the {\sc flock} 
algorithm is a special case of the simulated annealing
algorithm for finding the Bayesian maximum-{\em a-posteriori}
estimate from a marginalized form of the {\sc structure} model with no
admixture and non-correlated allele frequencies.

@@

Though we observed similar results
between the two programs at low values of $K$, {\sc flock}'s `best-run' solutions became somewhat inconsistent at higher values of $K$.
This observation was consistent with \citet{Duc&Tur2012}'s comparison of the 
two programs using simulated data 
for $K=4$ \& 8, $L=10$ (Fig. 4 in \citet{Duc&Tur2012}). 
This is likely a consequence of the rapidly increasing size of the search space over possible 
partitions as $K$ and $n$, the number of individuals, increase. 
The likelihood surface defined on partitions of this space will often
be multimodal---possessing numerous local peaks and troughs.
The peak that  {\sc flock}'s deterministic algorithm finds is entirely determined by the initial allocation of 
individuals, as it is a deterministic algorithm.
If the number of initial allocations does not increase
as $K$ is increased, the starting allocations become diffusely scattered in the space of all
possible partitions making it less likely that many (if any at all) will converge to the same local mode. 
This coupled with the fact that there is 
ambiguity in what defines a `best run' when all plateaus are of length zero complicates the interpretation
of results from {\sc flock} if no non-zero plateaus are encountered. The problem of getting 
caught in local modes is not unique to {\sc flock}---{\sc structure} also can converge to 
different solutions in complex spaces; however our results suggest this is a bigger problem for {\sc flock}.
By increasing the number of loci used in their simulations, \citet{Duc&Tur2012} showed  that 
{\sc flock} was able to converge in a simulated data set with $K=8$, but held no advantage in inference of $K$ over {\sc structure}. That simulated data set, with $n=240$ was considerably smaller and less complex than the real data investigated here.
%They simulated data using 500 individuals per population but only used 30 of them in the analysis.
% if you have more loci than individuals per population with high Fst between groups it does great!

@@

Often, newly-developed algorithms come to be understood within more general contexts and 
frameworks, and this, in turn, can help guide improvement of those algorithms.  For example, in population
genetics, the ``Markov recursion'' algorithm of \citet{Gri&Tav1994-AI} was identified by \citet{Felsensteinetal1999} 
as a special case of importance sampling \citep{Ham&Han1964}, a perspective which allowed 
\citet{Ste&Don2000} to improve upon the algorithm dramatically.  Here we have identified the {\sc flock}
algorithm as a limiting case of simulating annealing upon {\sc structure}'s no-admixture model with uncorrelated
allele frequencies. We hope this will
help users to understand and interpret {\sc flock}'s behavior and will provide insights that may be useful 
in the potential development of the {\sc flock} algorithm.

>>>>

However, here we identify 
the close relationship between {\sc flock}'s algorithm and the program
{\sc structure}.  Although the algorithm in {\sc flock}
is, as the authors point out, deterministic (apart from a random initial allocation of 
individuals to cluster), it can be interpreted as a 
limiting case of a probabilistic search algorithm applied to one of {\sc structure}'s
models.  More specifically, the {\sc flock} 
algorithm is a special case of the simulated annealing
algorithm for finding the Bayesian maximum-{\em a-posteriori}
estimate from a marginalized form of the {\sc structure} model with no
admixture and non-correlated allele frequencies.

@@

Though we observed similar results
between the two programs at low values of $K$, {\sc flock}'s `best-run' solutions became somewhat inconsistent at higher values of $K$.
This observation was consistent with \citet{Duc&Tur2012}'s comparison of the 
two programs using simulated data 
for $K=4$ \& 8, $L=10$ (Fig. 4 in \citet{Duc&Tur2012}). 
This is likely a consequence of the rapidly increasing size of the search space over possible 
partitions as $K$ and $n$, the number of individuals, increase. 
The likelihood surface defined on partitions of this space will often
be multimodal---possessing numerous local peaks and troughs.
The peak that  {\sc flock}'s algorithm finds is entirely determined by the initial, random, allocation of 
individuals, as it is a deterministic algorithm.
If the number of initial allocations does not increase
as $K$ is increased, the starting allocations become diffusely scattered in the space of all
possible partitions making it less likely that many (if any at all) will converge to the same local mode. 
This coupled with the fact that there is 
ambiguity in what defines a `best run' when all plateaus are of length zero complicates the interpretation
of results from {\sc flock} if no non-zero plateaus are encountered. The problem of getting 
caught in local modes is not unique to {\sc flock}---{\sc structure} also can converge to 
different solutions in complex spaces; however our results suggest this is a bigger problem for {\sc flock}.
By increasing the number of loci used in their simulations, \citet{Duc&Tur2012} showed  that 
{\sc flock} was able to converge in a simulated data set with $K=8$, but held no advantage in inference of $K$ over {\sc structure}. That simulated data set, with $n=240$ was considerably smaller and less complex than the real data investigated here.
%They simulated data using 500 individuals per population but only used 30 of them in the analysis.
% if you have more loci than individuals per population with high Fst between groups it does great!

@@

Often, newly-developed algorithms come to be understood within more general contexts and 
frameworks, and this, in turn, can help guide improvement of those algorithms.  For example, in population
genetics, the ``Markov recursion'' algorithm of \citet{Gri&Tav1994-AI} was identified by \citet{Felsensteinetal1999} 
as a special case of importance sampling \citep{Ham&Han1964}, a perspective which allowed 
\citet{Ste&Don2000} to improve upon the algorithm dramatically.  Here we have identified the {\sc flock}
algorithm as a limiting case of simulating annealing upon {\sc structure}'s no-admixture model with uncorrelated
allele frequencies. We hope this will
help users to understand and interpret {\sc flock}'s behavior and will provide insights that may be useful 
in the potential development of {\sc flock} or other clustering algorithms.

\section*{Acknowledgments}
We are grateful to Robin Waples for helpful comments on a draft of this paper.
